Affective Uplift During Video Game Play: A Naturalistic Case Study

### 2024-04-04 ms.Rmd
Fix reproducibility issues (#12)
* Fixes to reproducibility

* Data path in env

* Uncompress if not yet

* Correctly load env var

* Indicate phony targets

# Analyze a subset of participants if required 
# (for testing etc.; be careful)
dat <- dat |> 
  filter(
    pid %in%
      sample(
        unique(dat$pid), 
        size = length(unique(dat$pid)) * N_SUBSET_PROPORTION
      )
  )

>>>>

# Analyze a subset of participants if required 
# (for testing etc.; be careful)
N_SUBSET_PROPORTION <- as.numeric(Sys.getenv("N_SUBSET_PROPORTION", unset = 1))
dat <- dat |> 
  filter(
    pid %in%
      sample(
        unique(dat$pid), 
        size = length(unique(dat$pid)) * N_SUBSET_PROPORTION
      )
  )
